%% ========================================================================
%% IEEE Transactions Style Bibliography
%% Generated for: paper1 - ST-MBAN for CCVN V2I Precaching
%% Target Journal: IEEE Internet of Things Journal
%% ========================================================================


%% ********** Related Work — CIoV and Content-Centric Networking **********

\bibitem{1}
Zhou Su, Yilong Hui, Qing Yang, ``The Next Generation Vehicular Networks: A Content-Centric Framework,'' \textit{IEEE wireless communications}, 2017, doi: 10.1109/MWC.2017.1600195WC.
\bibitem{2}
Amuleen Gulati, G. Aujla, Rajat Chaudhary, Neeraj Kumar, M. Obaidat, ``Deep Learning-Based Content Centric Data Dissemination Scheme for Internet of Vehicles,'' \textit{2018 IEEE International Conference on Communications (ICC)}, 2018, doi: 10.1109/ICC.2018.8422427.
\bibitem{3}
M. Wang, Jun Wu, Gaolei Li, Jianhua Li, Qiang Li..., ``Toward mobility support for information-centric IoV in smart city using fog computing,'' \textit{2017 IEEE International Conference on Smart Energy Grid Engineering (SEGE)}, 2017, doi: 10.1109/SEGE.2017.8052825.
\bibitem{4}
Chengcheng Zhao, M. Dong, K. Ota, Jianhua Li, Jun Wu, ``Edge-MapReduce-Based Intelligent Information-Centric IoV: Cognitive Route Planning,'' \textit{IEEE Access}, 2019, doi: 10.1109/ACCESS.2019.2911343.
\bibitem{5}
Zhuo Li, Yutong Chen, Deliang Liu, Xiang Li, ``Performance analysis for an enhanced architecture of IoV via Content-Centric Networking,'' \textit{EURASIP Journal on Wireless Communications and Networking}, 2017, doi: 10.1186/S13638-017-0905-4.
\bibitem{6}
Shahzad Rizwan, G. Husnain, Farhan Aadil, Fayaz Ali, Sang-Kug Lim, ``Mobile Edge-Based Information-Centric Network for Emergency Messages Dissemination in Internet of Vehicles: A Deep Learning Approach,'' \textit{IEEE Access}, 2023, doi: 10.1109/ACCESS.2023.3288420.
\bibitem{7}
Ajay Kumar, A. Kalam, N. Hariharan, ``Enhanced Mobility Based Content Centric Routing In RPL for Low Power Lossy Networks in Internet of Vehicles,'' \textit{Annual Meeting of the IEEE Industry Applications Society}, 2020, doi: 10.1109/ICoIAS49312.2020.9081846.
\bibitem{8}
Irfanullah Khan, Tiankui Zhang, Xiaogeng Xu, Siyang Shan, Adil Khan..., ``Priority-based Content Dissemination in Content Centric Vehicular Networks,'' \textit{IEEE Advanced Information Management, Communicates, Electronic and Automation Control Conference}, 2018, doi: 10.1109/IMCEC.2018.8469332.
\bibitem{9}
Xiaonan Wang, Gaoyang Wu, ``Attributes Based Vehicular Named Data Networking for Driving Assistance,'' \textit{IEEE Transactions on Network Science and Engineering}, 2025, doi: 10.1109/TNSE.2025.3550154.
\bibitem{10}
Sajjad Ahmad Khan, Huhnkuk Lim, Shehzad Ashraf Chaudhry, ``Adaptive Data Forwarding Scheme for Diverse Infotainment Services in Vehicular Named Data Networking,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2024.3524122.
\bibitem{11}
Huhnkuk Lim, ``Toward Infotainment Services in Vehicular Named Data Networking: A Comprehensive Framework Design and Its Realization,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2025, doi: 10.1109/TITS.2024.3489574.
%% ********** Related Work — V2I Precaching **********

\bibitem{12}
Yinan Liu, Chao Yang, Xin Chen, Fengyan Wu, ``Joint Hybrid Caching and Replacement Scheme for UAV-Assisted Vehicular Edge Computing Networks,'' \textit{IEEE Transactions on Intelligent Vehicles}, 2024, doi: 10.1109/TIV.2023.3323217.
\bibitem{13}
Zilin Huang, Sikai Chen, Yuzhuang Pian, Zihao Sheng, Soyoung Ahn..., ``Toward C-V2X Enabled Connected Transportation System: RSU-Based Cooperative Localization Framework for Autonomous Vehicles,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2024, doi: 10.1109/TITS.2024.3410185.
\bibitem{14}
Wenlin Yao, Jiayi Liu, Chen Wang, Qinghai Yang, ``Learning-based RSU Placement for C-V2X with Uncertain Traffic Density and Task Demand,'' \textit{IEEE Wireless Communications and Networking Conference}, 2023, doi: 10.1109/WCNC55385.2023.10118783.
\bibitem{15}
Soohyun Park, C. Park, Soyi Jung, Minseok Choi, Joongheon Kim, ``Age-of-Information Aware Caching and Delivery for Infrastructure-Assisted Connected Vehicles,'' \textit{IEEE Transactions on Vehicular Technology}, 2024, doi: 10.1109/TVT.2024.3384952.
\bibitem{16}
Daud Khan, Sawera Aslam, Kyunghi Chang, ``Vehicle-to-Infrastructure Multi-Sensor Fusion (V2I-MSF) With Reinforcement Learning Framework for Enhancing Autonomous Vehicle Perception,'' \textit{IEEE Access}, 2025, doi: 10.1109/ACCESS.2025.3551367.
\bibitem{17}
Azan Khan, Basharat Hussain, Muhammad F. Islam, M. M. A. Dabel, Ali Kashif Bashir, ``Optimizing Content Cache With Vehicular Edge Computing: A Deep Federated Learning-Based Novel Predictive Study,'' \textit{IEEE transactions on consumer electronics}, 2025, doi: 10.1109/TCE.2025.3571029.
\bibitem{18}
Tengfei Cao, Ni Zhang, Xiaoying Wang, Jianqiang Huang, ``Mobility-Aware Cooperative Caching in Vehicular Edge Computing Based on Federated Distillation and Deep Reinforcement Learning,'' \textit{IEEE Transactions on Network Science and Engineering}, 2025, doi: 10.1109/TNSE.2025.3571902.
\bibitem{19}
Chao Xiang, Xiaopo Xie, Chen Feng, Zhen Bai, Zhendong Niu..., ``V2I-BEVF: Multi-modal Fusion Based on BEV Representation for Vehicle-Infrastructure Perception,'' \textit{2023 IEEE 26th International Conference on Intelligent Transportation Systems (ITSC)}, 2023, doi: 10.1109/ITSC57777.2023.10421963.
\bibitem{20}
Yali Wang, Shouhao Li, ``Federated Learning-based Vehicle Edge Caching Optimization Strategy,'' \textit{2025 IEEE 6th International Conference on Pattern Recognition and Machine Learning (PRML)}, 2025, doi: 10.1109/PRML66062.2025.11160265.
%% ********** Related Work — V2V Precaching **********

\bibitem{21}
Zhaolong Ning, Kaiyuan Zhang, Xiaojie Wang, Lei Guo, Xiping Hu..., ``Intelligent Edge Computing in Internet of Vehicles: A Joint Computation Offloading and Caching Solution,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2021, doi: 10.1109/TITS.2020.2997832.
\bibitem{22}
Yaodong Huang, Xintong Song, Fan Ye, Yuanyuan Yang, Xiaoming Li, ``Fair and Efficient Caching Algorithms and Strategies for Peer Data Sharing in Pervasive Edge Computing Environments,'' \textit{IEEE Transactions on Mobile Computing}, 2020, doi: 10.1109/TMC.2019.2902090.
\bibitem{23}
Yaodong Huang, Xintong Song, Fan Ye, Yuanyuan Yang, Xiaoming Li, ``Fair Caching Algorithms for Peer Data Sharing in Pervasive Edge Computing Environments,'' \textit{IEEE International Conference on Distributed Computing Systems}, 2017, doi: 10.1109/ICDCS.2017.151.
\bibitem{24}
Bishmita Hazarika, Keshav Singh, ``AFL-DMAAC: Integrated Resource Management and Cooperative Caching for URLLC-IoV Networks,'' \textit{IEEE Transactions on Intelligent Vehicles}, 2024, doi: 10.1109/TIV.2023.3303932.
\bibitem{25}
Zhu Jin, Tiecheng Song, Wen-Kang Jia, ``An Adaptive Cooperative Caching Strategy for Vehicular Networks,'' \textit{IEEE Transactions on Mobile Computing}, 2024, doi: 10.1109/TMC.2024.3367543.
\bibitem{26}
Arzoo Miglani, Neeraj Kumar, ``A Blockchain Based Matching Game for Content Sharing in Content-Centric Vehicle-to-Grid Network Scenarios,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2024, doi: 10.1109/TITS.2023.3322826.
\bibitem{27}
Yan Liang, Haijun Zhang, Xiying Fan, Yang Lu, Haojin Li..., ``Joint Optimization of Delay and Energy Consumption in Urban IoV: A Resource Allocation and Cooperative Caching Strategy,'' \textit{IEEE Transactions on Communications}, 2025, doi: 10.1109/TCOMM.2025.3597808.
\bibitem{28}
Yasin Habtamu Yacob, Guolin Sun, Hayla Nahom Abishu, Daniel Ayepah-Mensah, Mohamed Basher Omer..., ``AI-Native Collaborative Content Sharing in Blockchain-Empowered UAV-Assisted D2D Networks,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3578087.
\bibitem{29}
Chenlang Jin, Haipeng Yao, Ruze Cai, Tianle Mai, Jiaqi Xu..., ``SkyNDN Incentivizer: Enhancing Content Sharing in UAV Named Data Networking,'' \textit{IEEE Transactions on Mobile Computing}, 2026, doi: 10.1109/TMC.2025.3622224.
\bibitem{30}
Yuao Wang, Qianlin Hu, Yao Cheng, Gan Zheng, Hongbo Sun..., ``Fairness-Aware Cooperative Caching in Vehicular Networks: An Asynchronous Federated Learning and Attention-Enhanced Multiagent DRL Approach,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3607968.
%% ********** Related Work — Popularity-Based Precaching **********

\bibitem{31}
Mingzhe Chen, Mohammad Mozaffari, W. Saad, Changchuan Yin, M. Debbah..., ``Caching in the Sky: Proactive Deployment of Cache-Enabled Unmanned Aerial Vehicles for Optimized Quality-of-Experience,'' \textit{IEEE Journal on Selected Areas in Communications}, 2016, doi: 10.1109/JSAC.2017.2680898.
\bibitem{32}
Zhou Su, Yilong Hui, Qichao Xu, Tingting Yang, Jianyi Liu..., ``An Edge Caching Scheme to Distribute Content in Vehicular Networks,'' \textit{IEEE Transactions on Vehicular Technology}, 2018, doi: 10.1109/TVT.2018.2824345.
\bibitem{33}
Wanying Huang, Tian Song, Yating Yang, Yu Zhang, ``Cluster-Based Cooperative Caching With Mobility Prediction in Vehicular Named Data Networking,'' \textit{IEEE Access}, 2019, doi: 10.1109/ACCESS.2019.2897747.
\bibitem{34}
Yaqin Xie, Cheng Zhou, Zhongyu Liu, Yu Zhang, Jianyue Zhu..., ``Research on Cache Placement Optimization and Popularity-Based Content Prefetching Strategy in LEO Satellite Networks,'' \textit{IEEE Transactions on Green Communications and Networking}, 2026, doi: 10.1109/TGCN.2025.3570489.
\bibitem{35}
Hao Zheng, Zhigang Hu, Liu Yang, Aikun Xu, Meiguang Zheng..., ``Proactive Spatio-Temporal Request Prediction for Replica Placement in Edge-Cloud Computing,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3579618.
\bibitem{36}
Qichao Xu, Mengzhen Cheng, Jie Jin, Zhou Su, Dongfeng Fang..., ``Cooperative Edge Content Caching With Popularity Prediction in UAV-Assisted Vehicular Networks,'' \textit{IEEE Transactions on Network Science and Engineering}, 2026, doi: 10.1109/TNSE.2026.3658663.
%% ********** Related Work — Mobility Prediction-Based Precaching **********

\bibitem{37}
Peng Yang, Ning Zhang, Shan Zhang, Li Yu, Junshan Zhang..., ``Content Popularity Prediction Towards Location-Aware Mobile Edge Caching,'' \textit{IEEE transactions on multimedia}, 2018, doi: 10.1109/TMM.2018.2870521.
\bibitem{38}
Rongqing Zhang, Rui Lu, Xiang Cheng, Ning Wang, Liuqing Yang, ``A UAV-Enabled Data Dissemination Protocol With Proactive Caching and File Sharing in V2X Networks,'' \textit{IEEE Transactions on Communications}, 2021, doi: 10.1109/TCOMM.2021.3064569.
\bibitem{39}
Biqian Feng, Chenyuan Feng, Daquan Feng, Yongpeng Wu, Xianggen Xia, ``Proactive Content Caching Scheme in Urban Vehicular Networks,'' \textit{IEEE Transactions on Communications}, 2023, doi: 10.1109/TCOMM.2023.3277530.
\bibitem{40}
Syed Maaz Shahid, Jeehyeon Na, Sungoh Kwon, ``Incorporating Mobility Prediction in Handover Procedure for Frequent-Handover Mitigation in Small-Cell Networks,'' \textit{IEEE Transactions on Network Science and Engineering}, 2025, doi: 10.1109/TNSE.2024.3487415.
\bibitem{41}
Jinguo Cheng, Ke Li, Yuxuan Liang, Lijun Sun, Junchi Yan..., ``Rethinking Urban Mobility Prediction: A Multivariate Time Series Forecasting Approach,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2025, doi: 10.1109/TITS.2024.3498054.
\bibitem{42}
Chenglong Wang, Jun Peng, Lin Cai, Weirong Liu, Ziyu Zhao..., ``Mobility and Context-Aware Precaching Strategy Using Spatial-Temporal Informer for Vehicular Service,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3530699.
\bibitem{43}
Genghua Yu, Jian Wu, Rui Liu, Yixin He, Zhigang Chen..., ``Joint Cooperative Caching and UAV Trajectory Optimization Based on Mobility Prediction in the Internet of Connected Vehicles,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2024, doi: 10.1109/TITS.2024.3429305.
\bibitem{44}
Shao-Hung Cheng, Yen-Ting Shih, Ko-Chin Chang, ``Proactive Deployment of Cache-Enabled Aerial Base Stations for Optimized Energy-Delay Cost,'' \textit{IEEE International Symposium on Personal, Indoor and Mobile Radio Communications}, 2022, doi: 10.1109/PIMRC54779.2022.9977871.
\bibitem{45}
Youngju Nam, Hyeonseok Choi, Euisin Lee, ``Content Storage Management and Precaching Scheme in Content-Centric-Network-Based Internet of Vehicles,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2024.3522322.
\bibitem{46}
Zijia Zhao, Liang Zhao, Nan Wu, Lexi Xu, Na Lin..., ``A Collaborative Caching and Offloading Approach for Vehicular Edge Computing,'' \textit{IEEE Transactions on Sustainable Computing}, 2026, doi: 10.1109/TSUSC.2026.3666125.
%% ********** Related Work — Hybrid Precaching **********

\bibitem{47}
Nyothiri Aung, Sahraoui Dhelim, L. Chen, Abderrahmane Lakas, Wenyin Zhang..., ``VeSoNet: Traffic-Aware Content Caching for Vehicular Social Networks Using Deep Reinforcement Learning,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2023, doi: 10.1109/TITS.2023.3250320.
\bibitem{48}
Kai Jiang, Yue Cao, Yujie Song, Huan Zhou, Shaohua Wan..., ``Asynchronous Federated and Reinforcement Learning for Mobility-Aware Edge Caching in IoV,'' \textit{IEEE Internet of Things Journal}, 2024, doi: 10.1109/JIOT.2023.3349255.
\bibitem{49}
Zhoufan Liao, Pang Liu, Bin Zheng, Xiaoyong Tang, ``Context-Aware Proactive Edge Caching for Vehicular Edge Computing Based on Asynchronous Federated Learning,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3552682.
\bibitem{50}
Yue Zhang, Zhenyu Na, Shiyu Li, Bin Lin, Yun Lin..., ``Joint Service Caching and Task Offloading for Multi-UAV-Assisted Offshore Edge Computing Networks,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2025.3589880.
\bibitem{51}
Liang Xu, Kaitao Meng, Deshi Li, Rui Wang, Lele Cong, ``Adaptive Video Segment Precaching With Varying Travel Duration for Internet of Vehicles,'' \textit{IEEE Internet of Things Journal}, 2025, doi: 10.1109/JIOT.2025.3587768.
\bibitem{52}
Yue Yin, Tomoaki Ohtsuki, ``Multi-UAV-Assisted Emergency Caching Networks: UAV Location and NOMA Power Optimization,'' \textit{2024 IEEE 100th Vehicular Technology Conference (VTC2024-Fall)}, 2024, doi: 10.1109/VTC2024-Fall63153.2024.10757722.
%% ********** Related Work — ML/DL-Based Precaching **********

\bibitem{53}
Chunhe Song, Wenxiang Xu, Tingting Wu, Shimao Yu, P. Zeng..., ``QoE-Driven Edge Caching in Vehicle Networks Based on Deep Reinforcement Learning,'' \textit{IEEE Transactions on Vehicular Technology}, 2021, doi: 10.1109/TVT.2021.3077072.
\bibitem{54}
Shuai Zhang, Tianzhang Cai, Di Wu, Dominic A. Schupke, Nirwan Ansari..., ``IoRT Data Collection With LEO Satellite-Assisted and Cache-Enabled UAV: A Deep Reinforcement Learning Approach,'' \textit{IEEE Transactions on Vehicular Technology}, 2024, doi: 10.1109/TVT.2023.3336262.
\bibitem{55}
Pei-Ying Lin, Hsiao-Ting Chiu, Rung-Hung Gau, ``Machine Learning-Driven Optimal Proactive Edge Caching in Wireless Small Cell Networks,'' \textit{IEEE Vehicular Technology Conference}, 2019, doi: 10.1109/VTCSpring.2019.8746649.
\bibitem{56}
Kailun Wang, Na Deng, ``A Privacy-Protected Popularity Prediction Scheme for Content Caching Based on Federated Learning,'' \textit{IEEE Transactions on Vehicular Technology}, 2022, doi: 10.1109/TVT.2022.3179413.
\bibitem{57}
Zhenhao Tan, Bin Chen, Ruidong Li, Lei Yang, Xiaohua Xu, ``Efficient Cache Retrieving Scheme in VANET via Online Reinforcement Learning,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2025.3532836.
\bibitem{58}
Hind Gamil A. Elrahim, N. A. Malik, Kamaludin Bin Mohamad Yusof, ``Efficient Network Traffic Prediction: Harnessing Hybrid Neural Networks,'' \textit{2024 IEEE International Conference on Advanced Telecommunication and Networking Technologies (ATNT)}, 2024, doi: 10.1109/ATNT61688.2024.10719303.
\bibitem{59}
Yuanjun Zhang, Lipeng Zhu, Xian-song Pi, Haobin Mao, Zhenyu Xiao, ``Reinforcement Learning-based Position Optimization for Movable Antenna-Enabled Relay Communications,'' \textit{2025 IEEE International Conference on Communications Workshops (ICC Workshops)}, 2025, doi: 10.1109/ICCWorkshops67674.2025.11162371.
%% ********** Related Work — Snapshot/RSU-Local Learning Approaches **********

\bibitem{60}
M. Hasan, Nusrat Jahan, Mohd Zakree Ahmad Nazri, S. Islam, Muhammad Attique Khan..., ``Federated Learning for Computational Offloading and Resource Management of Vehicular Edge Computing in 6G-V2X Network,'' \textit{IEEE transactions on consumer electronics}, 2024, doi: 10.1109/TCE.2024.3357530.
\bibitem{61}
Xinran Zhang, Zheng Chang, T. Hu, Weilong Chen, Xin Zhang..., ``Vehicle Selection and Resource Allocation for Federated Learning-Assisted Vehicular Network,'' \textit{IEEE Transactions on Mobile Computing}, 2024, doi: 10.1109/TMC.2023.3283295.
\bibitem{62}
Ruichen Zhang, Changyuan Zhao, Hongyang Du, D. Niyato, Jiacheng Wang..., ``Embodied AI-Enhanced Vehicular Networks: An Integrated Vision Language Models and Reinforcement Learning Method,'' \textit{IEEE Transactions on Mobile Computing}, 2025, doi: 10.1109/TMC.2025.3582864.
\bibitem{63}
Namory Fofana, Asma Ben Letaifa, A. Rachedi, ``Intelligent Task Offloading in Vehicular Networks: A Deep Reinforcement Learning Perspective,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2024.3427814.
\bibitem{64}
R. Liu, Jianping Pan, ``CRS: A Privacy-Preserving Two-Layered Distributed Machine Learning Framework for IoV,'' \textit{IEEE Internet of Things Journal}, 2024, doi: 10.1109/JIOT.2023.3287799.
\bibitem{65}
Huaming Wu, Anqi Gu, Yonghui Liang, ``Federated Reinforcement Learning-Empowered Task Offloading for Large Models in Vehicular Edge Computing,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2024.3481876.
\bibitem{66}
Ashab Uddin, A. Sakr, Ning Zhang, ``Adaptive Prioritization and Task Offloading in Vehicular Edge Computing Through Deep Reinforcement Learning,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2024.3499962.
\bibitem{67}
Bo Xu, Haitao Zhao, Haotong Cao, Xiaozhen Lu, Hongbo Zhu, ``Joint Contract Design and Task Reorganization for Semi-Decentralized Federated Edge Learning in Vehicular Networks,'' \textit{IEEE Transactions on Vehicular Technology}, 2024, doi: 10.1109/TVT.2024.3364515.
\bibitem{68}
Qin Yang, Sang-Jo Yoo, ``Hierarchical Reinforcement Learning-Based Routing Algorithm With Grouped RSU in Urban VANETs,'' \textit{IEEE transactions on intelligent transportation systems (Print)}, 2024, doi: 10.1109/TITS.2024.3353258.
\bibitem{69}
Jinhai Zhang, Junwei Zhang, Zhuoru Ma, Teng Li, Xinghua Li..., ``RUPT-FL: Robust Two-Layered Privacy-Preserving Federated Learning Framework With Unlinkability for IoV,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2024.3511255.
\bibitem{70}
Wei Zhao, Tangjie Weng, Yu Cheng, Zhi Liu, Nei Kato, ``Deep Reinforcement Learning for Optimizing Multi-Hop Distributed Collaborative Task Offloading in R2X,'' \textit{IEEE Transactions on Vehicular Technology}, 2025, doi: 10.1109/TVT.2025.3538165.
\bibitem{71}
G. R. Gopal, Jie Chen, W. Hillery, Jun Tan, Serdar Özen..., ``Wireless Channel Scenario Identification Using Convolutional Neural Networks,'' \textit{IEEE Vehicular Technology Conference}, 2023, doi: 10.1109/VTC2023-Spring57618.2023.10200552.
\bibitem{72}
Ryota Imai, M. Hashimoto, Kazuhiko Takahashi, ``Distributed IMM-Based Cooperative Object Tracking Using Multiple Roadside LiDARs,'' \textit{IEEE Region 10 Conference}, 2025, doi: 10.1109/TENCON66050.2025.11375003.