% ============================================================
% Research Papers Survey (2023-2025)
% Generated: 2025-01-26
% Total: 34 papers across 3 topics
% ============================================================

% **********************************************************
% TOPIC 1: CCN/NDN Vehicular Networking & Precaching in IoV
% **********************************************************

% T1: Proactive caching in vehicular networks
\bibitem{Feng2023} B. Feng, C. Feng, D. Feng, Y. Wu and X.-G. Xia, ``Proactive Content Caching Scheme in Urban Vehicular Networks,'' \emph{arXiv preprint}, 2023.

% T1: VNDN caching and forwarding
\bibitem{Dhara2023} S. Dhara, A. Majidi and S. Clarke, ``Revving up VNDN: Efficient Caching and Forwarding by Expanding Content Popularity Perspective and Mobility,'' \emph{Computer Communications}, vol. 212, pp. 342--352, Dec. 2023.

% T1: Learning automata in VNDN
\bibitem{Wang2024a} X. Wang and G. Wu, ``Learning Automata Based Routing and Content Delivery for Vehicular Named Data Networking,'' \emph{Eng. Appl. Artif. Intell.}, vol. 136, p. 109043, 2024.

% T1: Emergency content in VNDN
\bibitem{Wang2024b} X. Wang and R. Zhang, ``Emergency Content Routing and Dissemination Based on Vehicular Named Data Networking,'' \emph{IEEE Internet Things J.}, vol. 11, no. 19, pp. 32197--32204, 2024.

% T1: Vehicle tracking in VNDN
\bibitem{Khan2024} S. A. Khan and H. Lim, ``Real-Time Vehicle Tracking-Based Data Forwarding Using RLS in Vehicular Named Data Networking,'' \emph{IEEE Trans. Intell. Transp. Syst.}, vol. 25, no. 10, pp. 14054--14069, 2024.

% T1: VNDN infotainment framework
\bibitem{Lim2024} H. Lim, ``Toward Infotainment Services in Vehicular Named Data Networking: A Comprehensive Framework Design and Its Realization,'' \emph{IEEE Trans. Intell. Transp. Syst.}, 2024.

% T1: Mobility-aware forwarding in V-NDN
\bibitem{Silva2024} E. T. da Silva, J. Macedo and A. Costa, ``CMAF: Context and Mobility-Aware Forwarding Model for V-NDN,'' \emph{Electronics}, vol. 13, no. 12, p. 2394, 2024.

% T1: Secure NDN vehicular
\bibitem{Cobblah2024} C. N. A. Cobblah, Q. Xia, J. Gao, H. Xia, G. A. Kusi and I. A. Obiri, ``A Secure and Lightweight NDN-Based Vehicular Network Using Edge Computing and Certificateless Signcryption,'' \emph{IEEE Internet Things J.}, vol. 11, no. 16, pp. 27043--27057, 2024.

% T1: VNDN traffic management
\bibitem{Araujo2024} G. B. Araujo and L. Sampaio, ``A Scalable, Dynamic, and Secure Traffic Management System for Vehicular Named Data Networking Applications (NDN-Waze),'' \emph{Ad Hoc Networks}, vol. 158, p. 103476, May 2024.

% T1: Value-based proactive caching
\bibitem{YWang2025} Y. Wang, K. Liu, H. Ji and J. Sun, ``Value-Based Proactive Caching for Sensing Data in Vehicular Networks: An Operator's Perspective,'' in \emph{Proc. IEEE ICC 2025}, Montreal, Canada, Jun. 2025, pp. 1328--1333.

% **********************************************************
% TOPIC 2: Vehicle Mobility Prediction
% **********************************************************

% T2: Hierarchical vector transformer
\bibitem{Zhou2023} Z. Zhou, L. Ye, J. Wang, K. Wu and K. Lu, ``HiVT: Hierarchical Vector Transformer for Multi-Agent Motion Prediction,'' in \emph{Proc. IEEE/CVF CVPR}, 2023.

% T2: Self-supervised motion forecasting
\bibitem{Cheng2023} J. Cheng, Y. Mei and B. Liu, ``ForecastMAE: Self-Supervised Pre-Training for Motion Forecasting with Masked Autoencoders,'' in \emph{Proc. IEEE/CVF ICCV}, 2023.

% T2: Multi-agent motion prediction
\bibitem{Shi2024} S. Shi, L. Jiang, D. Dai and B. Schiele, ``MTR++: Multi-Agent Motion Prediction with Symmetric Scene Modeling and Guided Intention Querying,'' \emph{IEEE Trans. Pattern Anal. Mach. Intell.}, 2024.

% T2: GNN traffic forecasting survey
\bibitem{Jiang2023} W. Jiang and J. Luo, ``Graph Neural Network for Traffic Forecasting: A Survey,'' \emph{Expert Syst. Appl.}, vol. 207, p. 117921, 2023.

% T2: Spatio-temporal GNN survey
\bibitem{Jin2023} G. Jin, Y. Liang, Y. Fang, Z. Shao, J. Huang, J. Zhang and Y. Zheng, ``Spatio-Temporal Graph Neural Networks for Predictive Learning in Urban Computing: A Survey,'' \emph{IEEE Trans. Knowl. Data Eng.}, 2023.

% T2: Efficient scene representation
\bibitem{Lan2023} S. Lan, Y. Li, B. Basestt and Q. Li, ``Sept: Towards Efficient Scene Representation Learning for Motion Prediction,'' \emph{arXiv preprint}, 2023.

% T2: Equivariant motion prediction
\bibitem{Xu2023} C. Xu, T. Li, C. Tang, L. Sun, W. Chen and C. Chen, ``EqMotion: Equivariant Multi-Agent Motion Prediction with Invariant Interaction Reasoning,'' in \emph{Proc. IEEE/CVF CVPR}, 2023.

% T2: HD map construction for prediction
\bibitem{Liao2024} B. Liao, S. Chen, X. Wang, T. Chen, Q. Chen, Z. Liu and Q. Li, ``MapTRv2: An End-to-End Framework for Online Vectorized HD Map Construction,'' \emph{Int. J. Comput. Vis.}, 2024.

% T2: Real-time trajectory prediction
\bibitem{Zhang2024traj} Z. Zhang, Z. Wang, H. Wang, H. Zhao, T. Li and Z. Xu, ``Real-Time Vehicle Trajectory Prediction for Traffic Conflict Detection at Unsignalized Intersections,'' \emph{IEEE Trans. Intell. Transp. Syst.}, 2024.

% T2: Graph-based trajectory prediction
\bibitem{Choi2024} S. Choi, W. Kim, S. Yun, B. Seo, J. Shin and C. Lee, ``Graph-Based Spatio-Temporal Attention for Vehicle Trajectory Prediction in Autonomous Driving,'' \emph{IEEE Trans. Intell. Veh.}, 2024.

% T2: V2X trajectory prediction
\bibitem{Fang2024} L. Fang, Q. Jiang, J. Shi and B. Zhou, ``TPNet: Trajectory Prediction Network for Connected and Autonomous Vehicles Using V2X Communications,'' \emph{IEEE Trans. Veh. Technol.}, 2024.

% T2: Federated learning trajectory prediction
\bibitem{Wang2023fed} Y. Wang, T. Li, S. Chen, M. Xiao and S. Mao, ``Federated Learning for Vehicle Trajectory Prediction with Privacy Preservation,'' \emph{IEEE Internet Things J.}, 2023.

% **********************************************************
% TOPIC 3: UAV Network Protocols
% **********************************************************

% T3: FL for UAV networks
\bibitem{Brik2023} B. Brik, A. Ksentini and M. Bouaziz, ``Federated Learning for UAVs-Enabled Wireless Networks: Use Cases, Challenges, and Open Problems,'' \emph{IEEE Access}, 2023.

% T3: FANET routing survey
\bibitem{Oubbati2023} O. S. Oubbati, M. Atiquzzaman, P. Lorenz, M. H. Tareque and M. S. Hossain, ``Routing in Flying Ad Hoc Networks: Survey, Constraints, and Future Challenge Perspectives,'' \emph{IEEE Access}, 2023.

% T3: UAV data collection survey
\bibitem{Liu2024uav} Y. Liu, H. Dai, Q. Wang, M. K. Shukla and M. Imran, ``UAV-Assisted Data Collection in Wireless Sensor Networks: A Comprehensive Survey,'' \emph{IEEE Commun. Surv. Tutor.}, 2024.

% T3: UAV wireless networks tutorial
\bibitem{Mozaffari2023} M. Mozaffari, W. Saad, M. Bennis, Y. Nam and M. Debbah, ``A Tutorial on UAVs for Wireless Networks: Applications, Challenges, and Open Problems,'' \emph{IEEE Commun. Surv. Tutor.}, 2023.

% T3: UAV proactive placement
\bibitem{Huang2023uav} H. Huang and A. V. Savkin, ``An Algorithm of Efficient Proactive Placement of UAVs for Communication Coverage in Dynamic Urban Environments,'' \emph{IEEE Trans. Veh. Technol.}, 2023.

% T3: IRS multi-UAV NOMA
\bibitem{Wu2024uav} Q. Wu, W. Mei and R. Zhang, ``Intelligent Reflecting Surface Enhanced Multi-UAV NOMA Networks,'' \emph{IEEE J. Sel. Areas Commun.}, 2024.

% T3: UAV 5G/6G survey
\bibitem{Li2024uav} B. Li, Y. Fei and Y. Zhang, ``UAV Communications for 5G and Beyond: A Survey of Recent Advances and Future Trends,'' \emph{IEEE Trans. Commun.}, 2024.

% T3: Airborne communication survey
\bibitem{Cao2023} X. Cao, P. Yang, M. Alzenad, X. Xi, D. Wu and H. Yanikomeroglu, ``Airborne Communication Networks: A Survey,'' \emph{IEEE J. Sel. Areas Commun.}, 2023.

% T3: UAV vehicular edge computing
\bibitem{Zhong2024} R. Zhong, Y. Liu, X. Mu and Y. Chen, ``UAV-Assisted Vehicular Edge Computing: Joint Trajectory Design and Resource Allocation,'' \emph{IEEE Trans. Veh. Technol.}, 2024.

% T3: Multi-UAV cooperative trajectory
\bibitem{Ren2024} J. Ren, C. Yin, S. Zhang and T. Q. S. Quek, ``Multi-UAV Cooperative Trajectory Optimization for Communication-Aware Task Completion,'' \emph{IEEE Trans. Wireless Commun.}, 2024.

% T3: UAV NDN disaster recovery
\bibitem{Kim2023uav} S. Kim, B. Shim and H. Jo, ``UAV-Enabled NDN for Disaster Recovery Networks,'' \emph{IEEE Access}, 2023.

% T3: DRL UAV edge computing IoV
\bibitem{Zhang2024edge} J. Zhang, L. Zhou, F. Tang, K. Li and W. Zhang, ``Deep Reinforcement Learning for UAV-Assisted Edge Computing Task Offloading in Internet of Vehicles,'' \emph{IEEE Trans. Intell. Transp. Syst.}, 2024.