\documentclass{article}
\usepackage[utf-8]{inputenc}

\begin{document}

\section*{Bibliography}

% ============================================================================
% SECTION 1: Self-Publications (Related Work Foundation)
% ============================================================================

\subsection*{Self-Publications by Authors}

\bibitem{Shin2020} 
Yongje Shin, Hyun-Seok Choi, Youngju Nam et al.. ``Data delivery protocol using the trajectory information on a road map in VANETs.'' 
\textit{Ad Hoc Networks}, 2020.

\bibitem{Nam2021} 
Youngju Nam, Hyun-Seok Choi, Yongje Shin et al.. ``Adaptive Content Precaching Scheme Based on the Predictive Speed of Vehicles in Content-Centric Vehicular Networks.'' 
\textit{Sensors}, 2021.

\bibitem{Shin2021} 
Yongje Shin, Hyunseok Choi, Youngju Nam et al.. ``Video Packet Distribution Scheme for Multimedia Streaming Services in VANETs.'' 
\textit{Sensors}, 2021.

\bibitem{Shin2022} 
Yongje Shin, Hyun-Seok Choi, Youngju Nam et al.. ``Particle Swarm Optimization Video Streaming Service in Vehicular Ad-Hoc Networks.'' 
\textit{IEEE Access}, 2022.

\bibitem{Choi2022a} 
Hyunseok Choi, Youngju Nam, Yongje Shin et al.. ``The partial cloud member replacement for reconstructing vehicular clouds in VANETs: Reactive and proactive schemes.'' 
\textit{Ad Hoc Networks}, 2022.

\bibitem{Mugerwa2022} 
Dick Mugerwa, Youngju Nam, Hyunseok Choi et al.. ``SF-Partition-Based Clustering and Relaying Scheme for Resolving Near-Far Unfairness in IoT Multihop LoRa Networks.'' 
\textit{Sensors}, 2022.

\bibitem{Nam2022a} 
Youngju Nam, Jaejeong Bang, Hyunseok Choi et al.. ``Cooperative Content Precaching Scheme Based on the Mobility Information of Vehicles in Intermittently Connected Vehicular Networks.'' 
\textit{Electronics}, 2022.

\bibitem{Nam2022b} 
Youngju Nam, Hyunseok Choi, Yongje Shin et al.. ``Expected Area-Based Real-Time Routing Protocol for Supporting Mobile Sinks in Wireless Sensor Networks.'' 
\textit{Electronics}, 2022.

\bibitem{Nam2022c} 
Youngju Nam, Hyunseok Choi, Yongje Shin et al.. ``RSU-Aided Optimal Member Replacement Scheme with Improved Mobility Prediction for Vehicular Clouds in VANETs.'' 
\textit{Electronics}, 2022.

\bibitem{Choi2022b} 
Hyunseok Choi, Youngju Nam, Yongje Shin et al.. ``Design and Evaluation of Schemes for Replacing Multiple Member Vehicles in Vehicular Clouds.'' 
\textit{Electronics}, 2022.

\bibitem{Nam2023a} 
Youngju Nam, Hyunseok Choi, Yongje Shin et al.. ``Traffic Optimized Content Precaching Scheme Based on Tolerable Delay Time in Content-Centric Vehicular Networks.'' 
\textit{IEEE Access}, 2023.

\bibitem{Mugerwa2023} 
Dick Mugerwa, Youngju Nam, Hyunseok Choi et al.. ``Implicit Overhearing Node-Based Multi-Hop Communication Scheme in IoT LoRa Networks.'' 
\textit{Sensors}, 2023.

\bibitem{Nam2023b} 
Youngju Nam, Jaejeong Bang, Hyunseok Choi et al.. ``Multiple Precaching Vehicle Selection Scheme Based on Set Ranking in Intermittently Connected Vehicular Networks.'' 
\textit{Sensors}, 2023.

\bibitem{Choi2024a} 
Hyunseok Choi, Yoonhyeong Lee, Gayeong Kim et al.. ``Resource Cluster-Based Resource Search and Allocation Scheme for Vehicular Clouds in Vehicular.'' 
\textit{Ad Hoc Networks}, 2024.

\bibitem{Mugerwa2024} 
Dick Mugerwa, Youngju Nam, Hyunseok Choi et al.. ``Adaptive Mobility-Based IoT LoRa Clustering Communication Scheme.'' 
\textit{Electronics}, 2024.

\bibitem{Shin2024} 
Yongje Shin, Hyun-Seok Choi, Youngju Nam et al.. ``Particle Swarm Optimization-Based Content Delivery Protocol for UAV VAENTs.'' 
\textit{IEEE Access}, 2024.

\bibitem{Choi2024b} 
Hyunseok Choi, Youngju Nam, Gayeong Kim et al.. ``Mobility-Based Multi-Hop Content Precaching Scheme in Content-Centric Vehicular Networks.'' 
\textit{Electronics}, 2024.

\bibitem{Nam2025} 
Youngju Nam, Hyunseok Choi, Euisin Lee. ``Content Storage Management and Precaching Scheme in Content-Centric-Network-Based Internet of Vehicles.'' 
\textit{IEEE Internet of Things Journal}, 2025.

\bibitem{Nam2026} 
Youngju Nam, Yongje Shin, Hyeonseok Choi et al.. ``Precaching vehicle selection based on soft actor-critic in CIoV.'' 
\textit{AIMS MATH}, 2026.

\bibitem{Shin2026} 
Yongje Shin, Hyunseok Choi, Youngju Nam et al.. ``PSO-Based Dynamic RSU Role Assignment Framework for Scalable and Reliable Content Delivery in VANETs.'' 
\textit{Sensors}, 2026.

\bibitem{Youn2026} 
Jongpil Youn, Youngju Nam, Euisin Lee. ``Dynamic Relay Assignment Scheme for Efficient V2V Content Precaching in Content-Centric Internet of Vehicles.'' 
\textit{Electronics}, 2026.


% ============================================================================
% SECTION 2: External References - Robust Optimization Foundations
% ============================================================================

\subsection*{Robust Optimization Theory}

\bibitem{Bertsimas2004} 
D. Bertsimas, Melvyn Sim. ``The Price of Robustness.'' 
\textit{Operational Research}, 2004, DOI: 10.1287/opre.1030.0065.


% ============================================================================
% SECTION 3: External References - Age of Information (AoI) Theory
% ============================================================================

\subsection*{Age of Information \& Real-Time Status Updates}

\bibitem{Yates2016} 
R. Yates, S. Kaul. ``The Age of Information: Real-Time Status Updating by Multiple Sources.'' 
\textit{IEEE Transactions on Information Theory}, 2016, DOI: 10.1109/TIT.2018.2871079.

\bibitem{Kaul2012} 
S. Kaul, R. Yates, M. Gruteser. ``Real-time status: How often should one update?.'' 
\textit{IEEE Transactions on Information Theory}, 2012.


% ============================================================================
% SECTION 4: External References - Vehicular Edge Caching (Recent 2024-2026)
% ============================================================================

\subsection*{Vehicular Edge Caching \& RSU Cooperative Strategies}

\bibitem{Wu2025a} 
Yiwen Wu, Fan Wu, Xiaoyan Huang et al.. ``Platoon-Based Edge Caching for Efficient Content Delivery in Vehicular Networks.'' 
\textit{2025 IEEE/CIC International Conference on Communications in China (ICCC)}, 2025, DOI: 10.1109/ICCC65529.2025.11149265.

\bibitem{Xu2026a} 
Qichao Xu, Mengzhen Cheng, Jie Jin et al.. ``Cooperative Edge Content Caching With Popularity Prediction in UAV-Assisted Vehicular Networks.'' 
\textit{IEEE Transactions on Vehicular Technology}, 2026.


% ============================================================================
% SECTION 5: External References - Content-Centric Networking (NDN/CCN in IoV)
% ============================================================================

\subsection*{Content-Centric \& Named Data Networking in IoV}

\bibitem{Gan2024} 
Yixin Gan, Rui Hou. ``Location-Based Clustering for Data Transmission in Vehicular Named Data Networking.'' 
\textit{2024 IEEE/CIC International Conference on Communications in China (ICCC)}, 2024, DOI: 10.1109/ICCC62479.2024.10681935.

\bibitem{Rizwan2024} 
Shahzad Rizwan, M. Ahmed, G. Husnain et al.. ``MACPE: Mobility Aware Content Provisioning in Edge Based Content-Centric Internet of Vehicles.'' 
\textit{IEEE Access}, 2024.


% ============================================================================
% SECTION 6: External References - V2V Relay & Cooperative Forwarding
% ============================================================================

\subsection*{V2V Relay \& Cooperative Forwarding Schemes}

\bibitem{Ji2025} 
Baofeng Ji, Kaipeng Sun, Weiguang Wang et al.. ``Relay Cooperative Vehicular Communication System: RIS-Equipped RF Source With Different Types of Forwarding Method.'' 
\textit{IEEE transactions on intelligent transportation systems (Print)}, 2025, DOI: 10.1109/TITS.2025.3539028.

\bibitem{Samantha2024} 
Beri Surya Samantha, Nitul Dutta, R. Mahadeva et al.. ``Graph Based Cooperative Forwarding in Information Centric Vehicular Networks.'' 
\textit{IEEE Transactions on Vehicular Technology}, 2024.


% ============================================================================
% SECTION 7: External References - ILP/MILP Optimization in Wireless Networks
% ============================================================================

\subsection*{Integer Linear Programming \& Optimization Methods}

\bibitem{Nie2025} 
Lili Nie, Huiqiang Wang, Guangsheng Feng et al.. ``DRL-MURA: A Joint Optimization of High-Definition Map Updating and Wireless Resource Allocation in Vehicular Edge Computing Networks.'' 
\textit{IEEE Internet of Things Journal}, 2025, DOI: 10.1109/JIOT.2024.3465553.

\bibitem{Cao2024} 
Xueyan Cao, Xiaolong Wu, Shuhan Zhang et al.. ``Intelligent Edge Computation and Trajectory Optimization in IRS-Enhanced UAV-Aided Vehicular Wireless Networks.'' 
\textit{IEEE Transactions on Vehicular Technology}, 2024.


% ============================================================================
% SECTION 8: External References - Coverage & Outage Mitigation
% ============================================================================

\subsection*{Coverage Hole \& Outage Zone Mitigation}

\bibitem{Jafari2025} 
Bahareh Jafari, M. Hasna, Nizar Zorba et al.. ``AI-Based Mitigation of Coverage Holes Through UAVs Path Planning.'' 
\textit{ICC 2025 - IEEE International Conference on Communications}, 2025, DOI: 10.1109/ICC52391.2025.11161018.

\bibitem{Yen2025} 
Kai Yen, Xiaojuan Zhang, Amnart Boonkajay et al.. ``Towards Resilient Nationwide Connectivity: Achievable Capacity of Non-Terrestrial Networks (NTN) for 5G/6G Integration.'' 
\textit{IEEE Communications Magazine}, 2025.


% ============================================================================
% SECTION 9: External References - Set Cover & Coverage Approximation Theory
% ============================================================================

\subsection*{Set Cover Problem \& NP-Hardness (Classical Theory)}

\bibitem{Ko2011} 
Ren-Song Ko. ``The Complexity of the Minimum Sensor Cover Problem with Unit-Disk Sensing Regions over a Connected Monitored Region.'' 
\textit{Int. J. Distributed Sens. Networks}, 2011, DOI: 10.1155/2012/918252.

\bibitem{Dumitrescu2013} 
A. Dumitrescu, Minghui Jiang. ``On the approximability of covering points by lines and related problems.'' 
\textit{Computational Geometry}, 2013, DOI: 10.1016/j.comgeo.2015.06.006.


\end{document}

%% 2025-2026 Recent Works on AoI-Guaranteed Precaching in CIoV
\bibitem{Wei2025}
  Jingrui Wei, Chenhao Shi, Yao Zhu, Yulin Hu, Anke Schmeink, ``Age-of-Information Minimization in Multi-Server Edge Computing Networks for URLLC Services,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2025.3566137.
\bibitem{Liang2025}
  Qingpeng Liang, Yanzhi Wu, ``Age of Information Optimization of Random Access Networks With Retry Limit,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2024.3525179.
\bibitem{Shan2025}
  Yingyi Shan, Ming Lei, Mingyu Hou, Mingyuan Wang, Minjian Zhao, ``The Age of Information in Barrage Relay Networks,'' 2025 IEEE 102nd Vehicular Technology Conference (VTC2025-Fall), 2025. doi: 10.1109/VTC2025-Fall65116.2025.11309931.
\bibitem{Shi2026}
  Kexin Shi, Yaru Fu, Yongna Guo, Fu Lee Wang, Tony Q. S. Quek, ``Age-of-Information and Latency Minimization for Cache-Enabled Mobile Crowdsensing Networks,'' IEEE Transactions on Vehicular Technology, 2026. doi: 10.1109/TVT.2025.3610162.
\bibitem{Xu2025}
  Ke Xu, Youyun Xu, Xiaoming Wang, Xianbin Wang, ``A Hybrid Collaborative Learning for Age of Information Minimization in Massive Access,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2024.3467255.
\bibitem{Ijaz2025}
  M. F. Ijaz, Umar Rashid, Omer Waqar, ``Beyond Single-User Scheduling: Exploiting Massive MIMO for Concurrent Data Delivery With Minimum Age of Information,'' IEEE Open Journal of Vehicular Technology, 2025. doi: 10.1109/OJVT.2024.3523247.
\bibitem{Zhang2025}
  Wentao Zhang, Yong Niu, Wenqing Li, Lei Xiong, Bo Ai, ``Age of Information Optimization in RIS-Assisted Multi-Cell Millimeter-Wave Communication Systems,'' 2025 IEEE 102nd Vehicular Technology Conference (VTC2025-Fall), 2025. doi: 10.1109/VTC2025-Fall65116.2025.11310602.
\bibitem{Gabr2025}
  Badiaa Gabr, Mustafa A. Kishk, ``Statistical Analysis for Average Peak Age of Information in LEO Satellite-Enabled IoT,'' 2025 IEEE 101st Vehicular Technology Conference (VTC2025-Spring), 2025. doi: 10.1109/VTC2025-Spring65109.2025.11174394.
\bibitem{Hu2025}
  Huimin Hu, Ruichen Zhang, Zhiguo Ding, Fan Jiang, Ruihong Jiang..., ``Optimizing AoI in RIS-Aided Wireless Powered Backscatter-Active Communication Networks,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2025.3565588.
\bibitem{Mei2025}
  Hao Mei, Haixia Zhang, Xiaotian Zhou, Jing Wang, ``AoI Minimization for Air–Ground Integrated Sensing and Communication Networks With Jamming Attack,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2025.3558061.
\bibitem{Li2025}
  Pan Li, Songtao Guo, Yue Zeng, Guiyan Liu, ``Joint Optimization of VNF Assignment and SFC Routing for Robust and Real-Time Symbiotic IoT Services,'' IEEE Internet of Things Journal, 2025. doi: 10.1109/JIOT.2025.3589522.
\bibitem{Yan2025}
  Ke Yan, Junjie Zhai, ``Multi UAV Collaborative Smoke Screen Planning under Full Occlusion Constraints: A Hybrid PSO Bayesian and ILP Computational Pipeline,'' 2025 IEEE 8th International Conference on Automation, Electronics and Electrical Engineering (AUTEEE), 2025. doi: 10.1109/AUTEEE67053.2025.11322263.
\bibitem{Hu2025}
  Lianhua Hu, Xiaofeng Yang, ``Hybrid Conflict-Driven Optimization for Multi-Robot Collaborative Transport Path Planning,'' Proceedings of the 2025 5th International Conference on Applied Mathematics, Modelling and Intelligent Computing, 2025. doi: 10.1145/3745533.3745568.
\bibitem{Ahmed2025}
  Md. Imtiaz Ahmed, Yaser Al Mtawa, ``Metaheuristic Optimization of Controller Placement in Software Defined Networks,'' International Conference on Wireless Communications and Mobile Computing, 2025. doi: 10.1109/IWCMC65282.2025.11059455.
\bibitem{Amir2026}
  Rida Amir, Haisem Naeem, Arshad Ali, M. Gulzar, ``MultiObjective Optimization in Wireless Mesh Networks – A Survey,'' ACM Computing Surveys, 2026. doi: 10.1145/3800685.
\bibitem{Padhy2025}
  Anita Padhy, ``SPOTSAFE: Preemptible-Aware Container Placement and Checkpoint Optimization for Hadoop YARN Optimization,'' 2025 2nd International Conference on Electronic Circuits and Signaling Technologies (ICECST), 2025. doi: 10.1109/ICECST66106.2025.11307235.
\bibitem{Ding2026}
  Guanyu Ding, Shiyu Yang, Han Lin, Zifan Chen, Jie-Si Yang, ``LLM-Driven Adaptive Cloud Resource Scheduling: Bridging Reasoning Intelligence With Optimization Guarantees,'' IEEE Open Journal of the Computer Society, 2026. doi: 10.1109/OJCS.2026.3667549.
\bibitem{Gao2025}
  Qian Gao, Quan Qiu, Yi Yin, Guoqiang Zhang, ``A MultiPath Forwarding Based Congestion Avoidance Strategy for Content Centric Networking,'' IEEE International Conference on Signal and Image Processing, 2025. doi: 10.1109/ICSIP65915.2025.11171608.
\bibitem{Khan2025}
  Y. Khan, R. N. B. Rais, Osman Khalid, I. Khan, ``A Latency-Aware and Resource-Efficient Content Caching Scheme for Content-Centric Networks,'' IEEE Access, 2025. doi: 10.1109/ACCESS.2025.3596376.
\bibitem{Nagai2025}
  Hitoshi Nagai, Rinji Murakami, Shinji Sugawara, ``Enhancing Content Availability and Consistency in Application-Layer CCN via RAID-like Redundancy,'' International Conference on Computational Intelligence and Intelligent Systems, 2025. doi: 10.1145/3787256.3787273.
\bibitem{Hodaka2025}
  Miyu Hodaka, Seiya Kubota, Shinji Sugawara, ``Maintaining Consistency During Content Updates Using CCN Control in Peer-To-Peer Networks,'' IEEE International Conference on Consumer Electronics, 2025. doi: 10.1109/ICCE63647.2025.10929888.
\bibitem{Dept2025}
  Sudarshan Dept, of Ece, Puornausri Rld, Priyanshi Dwivedi, ``Automated Pothole Detection and Repair Robot,'' 2025 International Conference on Emerging Technologies in Electronics and Green Energy (ICETEG), 2025. doi: 10.1109/ICETEG66194.2025.11473097.
\bibitem{Lu2025}
  Shuaibing Lu, Bojin Xiang, Jie Wu, Philipp Andelfinger, Wentong Cai, ``Multi-Timescale Hierarchical Prefetching for Online Caching in Vehicular Edge Networks,'' International Conference on Computer Communications and Networks, 2025. doi: 10.1109/ICCCN65249.2025.11133729.
\bibitem{Liu2025}
  Chang Liu, Zheng Xue, Canliang Liao, Jiawen Kang, Guojun Han, ``DRL-Enhanced Vehicular Edge Caching Addressing Content Dynamics and Complex Intersections,'' IEEE Internet of Things Journal, 2025. doi: 10.1109/JIOT.2024.3462479.
\bibitem{Zhang2025}
  De-gan Zhang, Wenjing Wang, Jie Zhang, Ting Zhang, Xuejie Ren..., ``New Method of Vehicular Network Content Distribution Based on Edge Caching and Catch Fish Optimization Strategy,'' IEEE Transactions on Reliability, 2025. doi: 10.1109/TR.2025.3617340.
\bibitem{Tang2025}
  Chaogang Tang, Huaming Wu, Ruidong Li, J. Rodrigues, ``Joint Optimization of Task Offloading Content Caching and Resource Allocation in Vehicular Edge Computing,'' ACM Transactions on Autonomous and Adaptive Systems, 2025. doi: 10.1145/3732782.
\bibitem{Lam2025}
  Thuong C. Lam, Nguyen-Son Vo, Minh-Phung Bui, C. D. T. Thai, Haejoon Jung..., ``Service Time-Aware Caching, Power Allocation, and 3D Trajectory Optimised Multimedia Content Delivery in UAV-Assisted IoT Networks,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2024.3510621.
\bibitem{Xu2025}
  Qichao Xu, Jie Jin, Zhou Su, Ruidong Li, Yuntao Wang..., ``Blockchain-Based Layered Secure Edge Content Delivery in UAV-Assisted Vehicular Networks,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2024.3505982.
\bibitem{Wang2025}
  Dazhi Wang, Siyuan Zhou, ``State-Aware Age of Information: Evaluating Content-Relevant Freshness in Wireless Systems,'' 2025 IEEE 102nd Vehicular Technology Conference (VTC2025-Fall), 2025. doi: 10.1109/VTC2025-Fall65116.2025.11310592.
\bibitem{Iloh2026}
  Divine Iloh, E. Osunwoke, Sadiq Adamu Abubakar, Grace Oku, Vennela Subramanyam..., ``ACORN-Edu: Deadline-Aware Prefetching for Learners With Intermittent Connectivity,'' IEEE Access, 2026. doi: 10.1109/ACCESS.2026.3668163.
\bibitem{Kim2025}
  Beom-Su Kim, ``Semantic-Aware Scheduling for Minimizing Age of Informative Data in WBAN-Based Health Monitoring Systems,'' IEEE Internet of Things Journal, 2025. doi: 10.1109/JIOT.2025.3529952.
\bibitem{Li2026}
  Yanjun Li, Yuzhe Chen, Jianji Shao, ``Dynamic Payload-Length-Aware Scheduling Strategies for Age Optimization in RF-Powered Ambient Backscatter Networks,'' IEEE Internet of Things Journal, 2026. doi: 10.1109/JIOT.2026.3651724.
\bibitem{Abreha2025}
  Haftay Gebreslasie Abreha, Ilora Maity, H. Chougrani, Christos Politis, S. Chatzinotas, ``On-Board Content Caching With Dynamic Cache Reconfiguration in Multi-Layer Satellite Edge Networks,'' IEEE Open Journal of the Communications Society, 2025. doi: 10.1109/OJCOMS.2025.3585451.
\bibitem{Wang2025}
  Chenglong Wang, Jun Peng, Lin Cai, Weirong Liu, Ziyu Zhao..., ``Mobility and Context-Aware Precaching Strategy Using Spatial-Temporal Informer for Vehicular Service,'' IEEE Internet of Things Journal, 2025. doi: 10.1109/JIOT.2025.3530699.
\bibitem{Ghosh2025}
  Sreya Ghosh, Sudipta Dey, Arijeet Ghosh, ``DQL-KSP: Deep Q-Learning assisted Knapsack-Based Cooperative Caching Framework for Vehicular Networks,'' 2025 2nd International Conference on Circuits, Power and Intelligent Systems (CCPIS), 2025. doi: 10.1109/CCPIS65231.2025.11233972.
\bibitem{Wang2025}
  Yuao Wang, Qianlin Hu, Yao Cheng, Gan Zheng, Hongbo Sun..., ``Fairness-Aware Cooperative Caching in Vehicular Networks: An Asynchronous Federated Learning and Attention-Enhanced Multiagent DRL Approach,'' IEEE Internet of Things Journal, 2025. doi: 10.1109/JIOT.2025.3607968.
\bibitem{Aldalbahi2025}
  Adel Aldalbahi, ``Proactive Edge Caching and Beam Management for mmWave Vehicular Networks,'' International Conference on Computing, Management and Telecommunications, 2025. doi: 10.1109/ComManTel68363.2025.11368547.
\bibitem{Feng2025}
  Chenyuan Feng, Zhenyu Feng, Jiaxin Yang, Tony Q. S. Quek, ``Simulation-Driven Analysis of AI-RAN Enabled Cooperative Content Delivery in Vehicular Networks,'' International Conference on Speech Technology and Human-Computer Dialogue, 2025. doi: 10.1109/ICCT67417.2025.11374126.
\bibitem{Em2025}
  Irina Em, Euisin Lee, ``Precaching Scheme based on Mobility and Caching Information of Vehicles in Intermittently Connected Vehicular Networks,'' 2025 8th International Conference on Information Communication and Signal Processing (ICICSP), 2025. doi: 10.1109/ICICSP66564.2025.11338208.
\bibitem{Doraiswamy2025}
  Vedha Vinodha Doraiswamy, M. Subramaniam, ``Traffic and Social Aware Content Caching in Vehicular Social Networks using Taylor Flamingo Shark Optimization,'' 2025 5th International Conference on Evolutionary Computing and Mobile Sustainable Networks (ICECMSN), 2025. doi: 10.1109/ICECMSN68058.2025.11382879.
\bibitem{Kim2025}
  C. Kim, Taeyoung Kim, Sukyoung Lee, ``Cooperative Service Caching for Reducing Delay in Multi-Edge Networks,'' IEEE Transactions on Vehicular Technology, 2025. doi: 10.1109/TVT.2024.3475585.
